\documentclass[12pt,a4paper]{iopart}

% Document information
\newcommand{\DRN}{CAS-PUB-MDL-000006}
\newcommand{\thisversion}{1.0}

% Author information
\input{common/authors/twhyntie.tex}

% Packages and settings for CERN@school document formatting
\input{common/tools/CERNatschool-packages.tex}

% CERN@school macros and definitions
\input{common/tools/defs.tex}

% Journal short-cuts.
\input{common/bib/journals}

\begin{document}

%
% Title
%
% The CERN@school logo
\input{common/tools/logoheader.tex}

%\title{\titlefont %
\title{%
The CERN@school Programme:\\
MoEDAL Grid User Guide%
}
% 
% Author information
\author{\theauthorinit$^{1, \, 2}$}
%
\address{$^1$\theauthoraddressA}
\address{$^2$\theauthoraddressB}
\ead{\mailto{\theauthoremail}}

%-----------------------------------------------------------------------------
% Abstract
\begin{abstract}
This document provides a guide to getting on the Worldwide LHC Computing Grid
(WLCG) with the Monopole and Exotics Detector at the LHC (MoEDAL)
experiment.
It covers what is required to get started on the Grid,
how MoEDAL is integrated with the WLCG infrastructure,
and how to run MoEDAL simulations using the GridPP DIRAC system and
Ganga User Interface.
\end{abstract}
%-----------------------------------------------------------------------------
%

{\color{white}Spacer}
\\[5cm]

% Add the license information (CC-BY-4).
\input{common/tools/licenseCCBY4}

\newpage

% Add a table of contents.
\setcounter{tocdepth}{2}
\tableofcontents

\newpage

%
% Introduction
%
\input{intro/intro}

\newpage

\input{bwb/bwb}

\newpage

\input{grid/grid}

\newpage

\input{sim/sim}

%\newpage

\input{next/next}

\newpage

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{References}
\label{sec:references}
\bibliographystyle{unsrt.bst}
\bibliography{MoEDAL,GridPP}
%
%------------------------------------------------------------------------------

\clearpage

\input{acronyms}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgements}
\label{sec:ack}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The author would like to thank MoEDAL Collaboration members
D. Felea (ISS/Bucharest), S. Baines (Uni. Manchester)
and J. Flores (Stony Brook Uni.) for support and documentation efforts,
and J. Pinfold (Uni. Alberta) and P. Mermod (Uni. Geneva) for
many fruitful discussions.
%
We are indebted to D. Bauer, S. Fayer (Imperial College London),
and J. Martyniak (now at RAL)
for their tremendous work developing and supporting GridPP \acs{DIRAC};
%
as well as the Ganga development team\footnote{%
See \href{https://github.com/ganga-devs/}{https://github.com/ganga-devs/}}
for their work on and support for the Ganga \ac{UI}.
Their combined efforts have transformed how small groups can
use the Grid and without them the work described here would not have been
possible.
%

This work was supported by the 
UK Science and Technology Facilities Council (STFC) 
via grant numbers 
ST/J000256/1 
and 
ST/N00101X/1,
as well as a Special Award from the Royal Commission for the Exhibition of 1851.
%
Computing resource and expertise was kindly provided by
the UK's GridPP Collaboration~\cite{gridpp2006,gridpp2009}\footnote{
\href{http://www.gridpp.ac.uk}{http://www.gridpp.ac.uk}}.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Version History}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%______________________________________________________________________________
\begin{table}[h]
\caption[Document version history]{\label{tab:version}Version history.}
\lineup
\begin{indented}
\item[]\begin{tabular}{@{}cllc}
\br
\centre{1}{$\quad$Version    $\quad$} & 
\centre{1}{$\quad$DOI        $\quad$} & 
\centre{1}{$\quad$Description$\quad$} &
\centre{1}{$\quad$Author     $\quad$} \\
\mr
1.0 & \href{http://doi.org/10.5281/zenodo.255649}{10.5281/zenodo.255649} & Initial version. & TW \\
\br
\end{tabular}
\end{indented}
\end{table}
%______________________________________________________________________________

\end{document}
